Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-03-13 draft.tex
Some tweaks to the two-column formatting in the appendix

\begin{widetext}
The correspondence between out choice of angular observables in the angular momentum basis, and the angular
observables as defined in reference \cite{Boer:2014kda} reads
\begin{equation}
\begin{aligned}
    8\pi S_{0, 0,  0} & = 1\,,                                                             &
    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
    8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
                      &                                                                    &
    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
%
    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           &
    8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
%
                      &                                                                    &
    8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
where the decay width is
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}\,.
\end{equation}

@@

To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta_2$, is not bounded from above.
This has to be considered if partial waves beyond the P-wave are included in the analysis, see e.g. \cite{Das:2014sra}.
However, our choice of basis is well suited to these applications with $0 \leq l < \infty$. Note, that the
physical range of $m$ is not affected by higher partial waves.

>>>>

The correspondence between out choice of angular observables in the angular momentum basis, and the angular
observables as defined in reference \cite{Boer:2014kda} reads
\begin{widetext}
\begin{equation}
\begin{aligned}
    8\pi S_{0, 0,  0} & = 1\,,                                                             &
    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
    8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
                      &                                                                    &
    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
%
    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           &
    8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
%
                      &                                                                    &
    8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
where the decay width is
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}\,.
\end{equation}

@@

To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta_2$, is not bounded from above.
This has to be considered if partial waves beyond the P-wave are included in the analysis, see e.g. \cite{Das:2014sra}.
However, our choice of basis is well suited to these applications with $0 \leq l < \infty$. Note, that the
physical range of $m$ is not affected by higher partial waves.\\
